---
output: 
  beamer_presentation:
    theme: "SwCustom"
title: "`r paste0('Draft report: ', params$client)`"
date: "`r Sys.Date()`"
toc: FALSE
classoption: aspectratio=169
editor_options: 
  chunk_output_type: console
params:
  data: NA
  client: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  comment = NA,
  fig.width = 14.22,
  fig.height = 8,
  fig.path = "figure/",
  out.width = "1.422\\textheight",
  out.height = ".8\\textheight",
  fig.align = "center",
  dpi = 600,
  results = "hide",
  error = FALSE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  dev = "CairoPNG"
)

library(dplyr)
library(scales)
library(ggplot2)
library(reshape2)
library(knitr)
library(Cairo)

dat <- 
  params$data %>%
  left_join(read.csv("../data/client_keys_2018_07_10.csv", header = TRUE, fileEncoding = "UTF-8-BOM"), 
            by= c("client_key" = "client_key"))

sw_green <- "#81bc00"
sw_purple <- "#410099"

```

## Analytics Notes

This is just a test report, designed to start the discussion about what we could show in a Google Analytics specific report for any given client. Here, I've used `r dat$client_name %>% unique()` as a test client.

**This is for internal use and discussion only.**

## Scope

* Client: `r dat$client_name %>% unique()`
    * Program: `r dat$program %>% unique()`
* Dates: `r min(dat$date)` to `r max(dat$date)`
* *N* rows: `r nrow(dat) %>% comma()`
* Total new users: `r sum(dat$newUsers) %>% comma()`
* Total sessions: `r sum(dat$sessions) %>% comma()`
* Average session length (min): `r (dat %>% filter(avg_session_duration_min > 0) %>% select(avg_session_duration_min) %>% summarize(xbar = mean(avg_session_duration_min)) %>% select(xbar) %>% first()) %>% round(1)`

## Google Analytics 

* `session` = A session is a group of user-page interactions that take place within a given time frame. A single session can contain multiple page views but will last no more than 30 minutes. 
    * if a user visits only *one page* during their session, Google Analytics considers the duration of that session as 0 minutes
* `new user` = User visiting site for the first time, identified by a Google Analytics "cookie"

## Daily users

```{r daily-users, echo = FALSE}

dat %>% 
  select(date, newUsers, existing_users) %>%
  melt(measure.vars = c("newUsers", "existing_users"), 
       variable.name = "user_type") %>%
  group_by(date, user_type) %>%
  summarize(tot_users = sum(value)) %>%
  ggplot(aes(x = date, y = tot_users, colour = user_type)) +
  geom_point(alpha = 0.5) +
  geom_smooth(se = FALSE) +
  scale_colour_manual(name = "User type", labels = c("New", "Existing"), 
                      values = c(sw_green, sw_purple)) +
  scale_y_continuous(labels = comma) +
  labs(x = "Date", y = "Total users") +
  theme(legend.position ="bottom")

```

## Daily users, day of week

```{r daily-users-day-of-week, echo = FALSE}

dat %>% 
  select(day_of_week, newUsers, existing_users) %>%
  melt(measure.vars = c("newUsers", "existing_users"), 
       variable.name = "user_type") %>%
  group_by(day_of_week, user_type) %>%
  summarize(n_users = sum(value)) %>%
  arrange(user_type, day_of_week) %>%
  group_by(user_type) %>%
  mutate(prop = n_users/sum(n_users)) %>%
  ggplot(aes(x = day_of_week, y = prop, fill = user_type)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_y_continuous(labels = percent) +
  labs(x = "Day of week", y = "Percent of users") +
  scale_fill_manual(name = "User type", labels = c("New", "Existing"), values = c(sw_green, sw_purple)) +
  theme(legend.position = "bottom")


```

## Hourly users

```{r hourly-users, echo = FALSE}

dat %>%
  group_by(hour) %>%
  summarize(tot_users = sum(users)) %>%
  mutate(prop = tot_users/sum(tot_users)) %>%
  ggplot(aes(x = hour, y = prop)) +
  geom_bar(stat = "identity", fill = sw_green) +
  scale_y_continuous(labels = percent) +
  labs(x = "Hour of day (24-hr)", y = "Percent of total users")

```

## Daily sessions, all users

```{r daily-ses, echo = FALSE}

dat %>%  
  group_by(date) %>%
  summarize(tot_sessions = sum(sessions)) %>%
  ggplot(aes(x = date, y = tot_sessions)) +
  geom_point(alpha = 0.5, color = sw_purple) +
  geom_smooth(se = FALSE, color = sw_purple) +
  scale_y_continuous(labels = comma) +
  labs(x = "Date", y = "Total sessions") 

```

## Cumulative sessions


```{r cum-session, echo = FALSE}

dat %>%  
  group_by(date) %>%
  summarize(tot_sessions = sum(sessions)) %>%
  arrange(date) %>%
  mutate(cum_sess = cumsum(tot_sessions)) %>%
  ggplot(aes(x = date, y = cum_sess)) +
  geom_line(color = sw_purple, lwd = 1) +
  scale_y_continuous(labels = comma) +
  labs(x = "Date", y = "Total sessions") 

```

## Average session length, day of week

```{r daily-ses-day-of-week, echo = FALSE, results = 'asis'}

dat %>%
  group_by(day_of_week) %>%
  filter(avg_session_duration_min > 0) %>%
  summarise(avg_session_duration_min = sum(avg_session_duration_min)/n()) %>%
  mutate(avg_session_duration_min = avg_session_duration_min %>% round(1)) %>%
  rename(Day = day_of_week, 
         `Mean session duration (min)` = avg_session_duration_min) %>% 
  kable()


```

## Average session length by hour 

```{r session-length-hour, echo = FALSE}

dat %>%
  group_by(hour) %>%
  filter(avg_session_duration_min > 0) %>%
  summarise(avg_session_duration_min = sum(avg_session_duration_min)/n(), 
            users = sum(users)) %>%
  ggplot(aes(x = hour, y = avg_session_duration_min)) +
  geom_bar(stat = "identity", fill = sw_green) +
  labs(x = "Hour of day (24-hr)", y = "Average session duration (min)")


```

## Hourly sessions

```{r hourly-ses, echo = FALSE}

dat %>%
  group_by(hour) %>%
  summarize(tot_sessions = sum(sessions)) %>%
  mutate(prop = tot_sessions/sum(tot_sessions)) %>%
  ggplot(aes(x = hour, y = prop)) +
  geom_bar(stat = "identity", fill = sw_green) +
  scale_y_continuous(labels = percent) +
  labs(x = "Hour of day (24-hr)", y = "Percent of total sessions")

```

## Sessions/user, date

```{r hourly-ses-user, echo = FALSE}

dat %>%
  group_by(date) %>%
  summarize(tot_users = sum(users), 
            tot_ses = sum(sessions)) %>%
  mutate(ses_per_user = tot_ses/tot_users) %>%
  ggplot(aes(x = date, y = ses_per_user)) +
  geom_point(alpha = 0.5, color = sw_purple) +
  geom_smooth(se = FALSE, color = sw_purple) +
  scale_y_continuous(labels = comma) +
  labs(x = "Date", y = "Sessions/user") 

```

## Page views

```{r daily-pageviews, echo = FALSE}

dat %>% 
  group_by(date) %>%
  summarize(page_views = sum(uniquePageViews)) %>%
  ggplot(aes(x = date, y = page_views)) +
  geom_point(alpha = 0.5, col = sw_purple) +
  geom_smooth(se = FALSE, col = sw_purple) +
  scale_y_continuous(labels = comma) +
  labs(x = "Date", y = "Total unique page views")

```

## Cumulative page views

```{r cumsum-pageviews, echo = FALSE}

dat %>% 
  group_by(date) %>%
  summarize(page_views = sum(uniquePageViews)) %>%
  arrange(date) %>%
  mutate(cumsum = cumsum(page_views)) %>%
  ggplot(aes(x = date, y = cumsum)) +
  geom_line(col = sw_purple, lwd = 1) +
  scale_y_continuous(labels = comma) +
  labs(x = "Date", y = "Total page views")

```


## Page views, day of week

```{r pageviews-day-of-week, echo = FALSE}

dat %>% 
  group_by(day_of_week) %>%
  summarize(page_views = sum(uniquePageViews)) %>%
  mutate(prop = page_views/sum(page_views)) %>%
  ggplot(aes(x = day_of_week, y = prop)) +
  geom_bar(stat = "identity", fill = sw_green) +
  scale_y_continuous(labels = percent) +
  labs(x = "Day of week", y = "Percent of page views")

```

## Unique page views/hour

```{r hourly-pageviews, echo = FALSE}

dat %>%
  group_by(hour) %>%
  summarize(page_views = sum(uniquePageViews)) %>%
  mutate(prop = page_views/sum(page_views)) %>%
  ggplot(aes(x = hour, y = prop)) +
  geom_bar(stat = "identity", fill = sw_green) +
  scale_y_continuous(labels = percent) +
  labs(x = "Hour of day (24-hr)", y = "Percent of page views")

```
